Dynamics of Laterally Propagating Flames in X-ray Bursts

### 2019-08-13 xrb/paper.tex
switch to aastex 6.3
update ORCiDs
update the end discussion

%\documentclass[12pt, preprint]{aastex}
\documentclass[preprint,times,tighten]{aastex62}

@@

\author{Donald Willcox}
\affiliation{Lawrence Berkeley National Laboratory, Berkeley, CA}

@@

\author{Max P.\ Katz}
\affiliation{Nvidia Corp}

@@

\author{Weiqun Zhang}
\affiliation{Lawrence Berkeley National Laboratory, Berkeley, CA}

@@

On the algorithmic front, we are exploring a change of our
hydrodynamics and reactive coupling to eliminate splitting error from
the traditional Strang splitting used in \castro\ and other
hydrodynamics codes.  One advantage of this is that the new algorithm
would be more amenable to offloading onto GPUs, a development task
that is underway.  Additionally, we will move to fourth-order accurate
methods and incorporate well-balanced reconstruction to better capture
the burning.

MHD, radiation transport, GPUs

>>>>

%\documentclass[12pt, preprint]{aastex}
\documentclass[preprint,times,tighten]{aastex63}

@@

\author[0000-0003-2300-5165]{Donald Willcox}
\affiliation{Lawrence Berkeley National Laboratory, Berkeley, CA}

@@

\author[0000-0003-0439-4556]{Max P.\ Katz}
\affiliation{NVIDIA Corp}

@@

\author[0000-0001-8092-1974]{Weiqun Zhang}
\affiliation{Lawrence Berkeley National Laboratory, Berkeley, CA}

@@

There are several changes we will pursue to the algorithm used to
model these XRBs.  First, as shown in \citet{castro_sdc}, we have
developed a fourth-order (in space and time) method for coupling
hydrodynamics and reactions that should greatly improve the accuracy
of the simulations.  We expect that by using this new high-order
algorithm we can drop a level of refinement from the simulations while
still accurately modeling the evolution.  We have also ported
\castro\ to GPUs, giving an order of magnitude performance boost on
nodes with both CPUs and GPUs.  The GPU-enabled algorithm will
increase the performance, allowing us to run bigger domains and/or
eliminate the boosting used here.

MHD, radiation transport
